---
title: "HFT_use"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HFT_use}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# High-Frequency Trading with mt5R

It's an pretty **naive** example to check the viability of high-frequency trading.

# How we will test it

We will run `100` times the function `MT5.Quick_GetSymbol()` too check how long will take every loop, and will calculate how many times this function will be used in **1 second** interval.

`Sending order > MT5 fetching data > Receiving data`, for every loop.

First let's load `mt5R`.

```{r setup}
library(mt5R)
```

Run the loop.

```{r}
iCnt <- 0; dtVec <- as.integer()

while(iCnt < 100)
{
  TableEx <- MT5.Quick_GetSymbol("EURUSD", iTF = 1, iRows = 10)
  dtVec[iCnt <<- iCnt + 1] <- Sys.time()
}
```

What is inside of `TableEx`?

```{r}
print(TableEx)
```

Now we will check the results.

```{r}
Dates <- as.POSIXct(dtVec, origin = "1970-01-01")
Secs <- as.integer(strftime(Dates, format = "%S")) ##Interested only on seconds
table(Secs)
```

Only one second interval was fully used - the middle one.

Answering the first question, how many times inside of 1 second the function `MT5.Quick_GetSymbol()` was used?

```{r}
InterestedNumber <- table(Secs)[2]
print(InterestedNumber[[1]]) ##only the number
```

How long, in average, `MT5.Quick_GetSymbol()` takes in **milliseconds** every run?

```{r, message=T}
1000/InterestedNumber[[1]]
```

The result is relative for every spec and parameters.

This was a naive example, focused in fetch data. Expert Advisors use a lot of computation, functions and every kind of models. The result demonstrate how powerful its the socket connection.
