---
title: "ListAllSymbols"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ListAllSymbols}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# List all symbols and types

Simple example to obtain all available symbols in MT5 marketwatch and theirs types (CFD, Forex, etc).

Load `mt5R` package.

```{r setup}
library(mt5R)
```

Use `MT5.Marketwatch()` to obtain all marketwatch symbols.

```{r}
AllSymbols <- MT5.Marketwatch()
print(AllSymbols)
```

Create a data.frame to summary all the data.

```{r}
df_symbols <- data.frame(Symbol = AllSymbols, Type = NA)
```

Use `MT5.SymbolType` to obtain the type of every symbol using loop.

```{r}
for(i in seq_len(dim(df_symbols)[1]))
{
  df_symbols[i,2] <- MT5.SymbolType(df_symbols[i,1])
}
```

* Types (check **Reference** tab for more details of `MT5.SymbolType`)
  + `-1` not found.
  + `0` is stock.
  + `1` is option.
  + `2` is future contract.
  + `3` is Forex.
  + `4` is CFD.

```{r}
print(df_symbols)
```


